---
title: "Analysis of purchases of mobile applications"
author: "Micha³ Sza³añski, Tuan Doan, Aleksandra Bednarczuk"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### 1. INTRODUCTION


##### 1.1. WEB APPLICATIONS


##### 1.2. DATASET


The dataset about Google play store apps was downloaded from kaggle.com website (to see the source click [here](https://www.kaggle.com/lava18/google-play-store-apps?fbclid=IwAR0ovxDCXAqDkyunIhSRKqKWRbX5KXnjR33KL_RUroKBwc1dcf5D_h5572A)). 


The dataset before cleaning had almost 11 thousand observations - mobile applications, and 13 variables - Application name, Category, Rating, Reviews, Size, Installs, Type, Price, Content Rating, Genres, Last Updated, Current version, Android version. After cleaning, the dataset remained 9367 observations and 11 variables - we rejected Category and Current version. The procedure of cleaning the data is saved and attached to the project in the file code.R.


### 2. EXPLORATORY DATA ANALYSIS


##### 2.1. BASIC STATISTICS


##### 2.2. MODELLING



```{r}

```

### 3. CONCLUSIONS


### 4. REFERENCES
